Make any stupid plot you want

### 2021-01-01 draft/sections/abstract.tex

The difference between drawing and data visualization is that visualization implies that some structure of the data is preserved in the visual presentation. We formalize what structure is preserved and how via a mathematical topological artist model. In our model, data and graphics can be viewed as sections of fiber bundles; this allows for (1) decomposing the translation of data fields (variables) into visual channels via an equivariant map on the fibers and (2) a topology-preserving map of the base spaces that encode the connectivity of the points in the dataset and elements of the graphic. Furthermore, this model supports an algebraic sum operation such that more complex visualizations can be built from simple ones. We illustrate the application of the model through case studies of a scatter plot, line plot, and heatmap. We show that this model can be implemented with a small prototype.

>>>>

The difference between drawing and data visualization is that visualization implies that some structure of the data is preserved in the visual presentation.* We formalize what structure is preserved and how via a mathematical topological artist model. In our model, data and graphics can be viewed as sections of fiber bundles; this allows for (1) decomposing the translation of data fields (variables) into visual channels via an equivariant map on the fibers and (2) a topology-preserving map of the base spaces that encode the preserving the dataset connectivity into graphical elements. Furthermore, this model supports an algebraic sum operation such that more complex visualizations can be built from simple ones. We illustrate the application of the model through case studies of a scatter plot, line plot, and heatmap. We show that this model can be implemented with a small prototype.
